A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-01 ECCV/paper.tex
Added blur direction image and done other corrections

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}
Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amount of blur.   In particular, we assume that scene motion 
blur be modelled locally as a linear motion blur~\cite{}.  Under this assumption,
scene content perpendicular to the blur direction is unaffected by the blur.  Because
of our circular design, this means the perpendicular direction can be observed as a 
unblurred linear pattern.  Figure X shows an example with various motion directions.

@@

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text(for real) = \pi/2 (for imaginary part)$. 
Then L2 norm of outputs along all orientations is calculated and finally, L2
normed image is binarized.

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{overall_flow.pdf}
\caption{Overall Workflow}
\end{figure}
Our fiducial detection strategy is different from \cite{NaimarkF02,Pitag13} and works
under significant amount of blur.   In particular, we assume that scene motion 
blur be modelled locally as a linear motion blur~\cite{}.  Under this assumption,
scene content perpendicular to the blur direction is unaffected by the blur.  Because
of our circular design, this means the perpendicular direction can be observed as a 
unblurred linear pattern.  Figure \ref{fig:blur_direction} shows an example with
various motion directions.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{blur_direction.pdf}
\caption{Relation of blur direction and unblurred linear pattern}
\label{fig:blur_direction}
\end{figure}

@@

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$). We have used following parameters for
creating each Gabor kernel: $\lambda = 8$, $\gamma = 0.5$, $\sigma =
0.56\lambda$, $\psi = 0 \text{(for real part)}, \pi/2 \text{(for imaginary
part)}$.
Then L2 norm of outputs along all orientations is calculated and finally, L2
normed image is binarized.
